%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.7in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{0.9in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-2pt}\scshape\raggedright{\large}
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-9pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-3pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.1in, label={}]\vspace{-3pt}}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-8pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    \textbf{\LARGE \scshape Chirag Soni} \\ \vspace{1pt}
    \small +91 7737672266 $|$ \href{mailto:sonichirag1999@gmail.com}{\underline{sonichirag1999@gmail.com}} $|$ 
    \href{https://linkedin.com/in/chirag-soni01/}{\underline{ linkedin.com/in/chirag-soni01}} 
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Indian Institute of Technology (BHU)}{Varanasi, India}
      {Bachelor of Technology in Metallurgical Engineering}{Jul 2017 -- May 2021}
  \resumeSubHeadingListEnd
%


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{Druva Data Solutions} $|$ Go, AWS, Distributed Systems}{May 2022 -- Present}
    \resumeSubSubheading
      {Software Engineer}{Pune, India}
      \resumeItemListStart
        \resumeItem{\textbf{Daintree Team}: Working on Druva’s nexgen storage system. Managing data, deduplication \& file systems.}
        \resumeItem{\textbf{Debugger Tool}: Developed an innovative internal command line interface (CLI) similar as git for the product file
system resulting in debugging and evaluating various types of data as per requirements, reducing developers effort for creating custom scripts.}
 \resumeItem{\textbf{API Signature Validation}: Implemented API’s security validation feature using AWS Paramstore and cryptography for
signing API cookies and identifying any possible security vulnerabilities.}
        \resumeItem{\textbf{Cloudcache Development}: Contributed to the development an on-premise software appliance that
optimizes backup and restores. Reduced backup and restore time by 30\%, improving data protection and
minimizing downtime.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    HCL
%-------------------------------------------

    \resumeProjectHeading
      {\textbf{HCL Technologies} $|$ Python, Machine Learning}{Jun 2021 -- Apr 2022}
      \resumeSubSubheading
      {Software Engineer}{Noida, India}
      \resumeItemListStart
        \resumeItem{\textbf{R\&D}: Development in the field of Topological Data Analysis (TDA) for identifying credit card transaction frauds achieving 92\% accuracy and used confusion matrix to view model’s performance.}
        \resumeItem{\textbf{Report Extracter}: Developed an innovative tool to extract data from unstructured data reports and aligning data
as per requirements using SGD optimizer to classify the required information and parsed data as per the required
format structure by closely working in a team taking initiative on innovation and future of the project.}
    \resumeItemListEnd


% -----------Multiple Positions Heading-----------
%    Joinsahara.com
%-------------------------------------------

    \resumeProjectHeading
      {\textbf{Joinsahara.com} $|$ Python, Natural Language Processing}{May 2020 -- Jun 2020}
      \resumeSubSubheading
      {Software Development Engineer Intern}{Remote}
      \resumeItemListStart
        \resumeItem{\textbf{Sentiment Analysis Engine}: Devised an algorithm to get sentiment and count of predefined sets of 5 aspect
categories of Amazon clothing reviews using Spacy for data processing and NLTK+Vader for
sentiment analysis resulting in making a
better online shopping experience.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Instagram Clone} $|$ \emph{JavaScript, React Native, Redux, Firebase, Expo}}{Jan 2021 -- Feb 2021}
          \resumeItemListStart
            \resumeItem{Created a hybrid Instagram-like social media mobile application using React-Native framework
for Android and IOS devices.}
            \resumeItem{App allows users to post images with description on their profile and allows them to interact
with other posts by 'liking', 'commenting', 'saving', and 'following', real-time 'messaging' to
different users’ accounts.}
            \resumeItem{Utilized Firestore for storing data on the signup page such as username, email ID, password
and profile picture.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Inventory Management of a Marketplace} $|$ \emph{PHP, HTML, MySQL, DBMS, JavaScript}}{Dec 2018 – Jan 2019}
          \resumeItemListStart
            \resumeItem{Developed a sample website for entries of a marketplace in the database.}
            \resumeItem{Three tables were created in the database which organized buying, selling of goods and
updating current stock on Apache server.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Go, C++, Python, Java, JavaScript, MySQL, Shell.} \\
     \textbf{Tools \& Technologies}{: ReactJs, React-native, DBMS, SQL, Linux, Docker, Jira, Git, VS Code} \\
     \textbf{Cloud}{: AWS, S3, DyanmoDB, CloudWatch, Microservices}
    }}
 \end{itemize}
 
%-----------Awards-----------
\section{Awards}
    \resumeSubHeadingListStart
      \resumeProjectHeading
        {\textbf{Winner of Druva Hackathon}}{Jan 2023}
          \resumeItemListStart
            \resumeItem{Led winning team in Druva’s company-wide hackathon with 200+ participants.}
            \resumeItem{Developing a new
data resiliency solution saving around 15K dollars per month, by listing S3 head objects and storing metadata in inhouse S3 wrapper called hubble.}
            \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{HCL ERS Champion Award}}{Aug 2022}
          \resumeItemListStart
            \resumeItem{Demonstrated the versatility to achieve more than expected accuracy by efficiently implementing algorithm using Topological Data Analysis.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
%





%-------------------------------------------
\end{document}
